Tree regeneration in models of forest dynamics: a key priority for further research

### 2023-04-28 manuscript/manuscriptRW.Rmd
change of one word in the manuscript

Tree regeneration arises from multiple processes such as pollination,
fruit maturation, seed production, dispersal, germination, juvenile
growth and survival [@price2001; @vacchiano2018]. All these processes
are difficult to assess, and some of them are scarcely understood and
thus appear highly stochastic [@bogdziewicz2021]. Identifying the
appropriate level of complexity for the mathematical formulation of the
key factors that are leading to successful tree regeneration is
challenging. Currently, tree regeneration processes in dynamic forest
models are handled in a multitude of ways [@konig_tree_2022;
@bugmann2022]: from 1) entirely ignoring it [as done in classical forest
growth models, e.g., Pretzsch et al. -@pretzsch2002], across 2) the use
of a few simple environmental filters, as done in most forest "gap"
models [@shugart1984] and Dynamic Global Vegetation Models [e.g.,
@hickler2012; @smith2001], to 3) complex approaches that incorporate
local feedback from the canopy, multiple ecological processes and often
also short time steps [e.g., @seidl2012; @wehrli2006], or 4) field-based
statistical parameterizations, which however are not easy to extrapolate
in space and time [e.g., @ribbens1994]. Overall, models are needed to
(1) synthesize existing empirical data and explore their relationships,
(2) assess future tree regeneration e.g. in the context of global change
scenarios, and (3) identify the most important processes that are
shaping ecological patterns. Given the current strategies that are used
in models of forest dynamics to represent tree regeneration, model
behavior often is prone to problems, such as very high levels of tree
regeneration that necessitate excess mortality at early stages of tree
life to simulate correct stand structure and composition. Also,
inadequately high species diversity in tree regeneration may be
simulated, which is characteristic of "classical" forest gap models
[@gutiérrez2016], at least as long as the simulation set-up comprises a
multitude of species. Some models use calibration against local
canopy-level data to constrain simulated regeneration levels, which is
likely to hamper the general applicability of these models e.g. under
scenarios of climate change. Furthermore, correctly capturing the
species composition in tree regeneration as a function of the presence
of seed trees in the canopy is often a particular challenge, potentially
leading to unrealistic successional drift in the model, which must be
corrected by factors that are hard to parameterize [e.g., @lischke2006].
A related issue is the excessive reduction of species diversity due to
positive feedback effects, such that eventually just single-species
stands remain. This is sometimes corrected by the incorporation of a low
level of seed influx of all species at all times [@schumacher2006] or by
restricting the number of seeds per species in the seedbank
[@lischke2006]. However, simulated species composition is usually
exceedingly sensitive to assumptions about seed availability, whereas
the parameters of such functions are poorly constrained by field data.
Lastly, there is often a problem with insufficient observational
constraints on parameter values for models that start from very small
tree sizes (e.g., 10 cm of height or even seeds) and track tree
development in a process-oriented manner by considering a multitude of
ecological influences, rather than emphasizing tree regeneration into a
larger size class [e.g., @wehrli2006].

@@

```{r mortality13, echo=FALSE, fig.cap="Ratio of tree regeneration between the 7 and 10 cm thresholds (regeneration 7 cm / regeneration 10 cm) and the overestimation proportion at 7 cm ([simulated -observed] / observed) for the mean regeneration per model across sites and samples. The horizontal dashed lines show a ratio equal to 1, indicating no decrease of regeneration between 7 and 10 cm, and a ratio equal to 1.77 corresponding to the Reineke self-thinning line under even-aged conditions. The vertical line indicates zero overestimation.", out.width='80%'}
knitr::include_graphics(here::here("figures", "mort7_10_medianOver.png"))
```

>>>>

Tree regeneration arises from multiple processes such as pollination,
fruit maturation, seed production, dispersal, germination, juvenile
growth and survival [@price2001; @vacchiano2018]. All these processes
are difficult to assess, and some of them are scarcely understood and
thus appear highly stochastic [@bogdziewicz2021]. Identifying the
appropriate level of complexity for the mathematical formulation of the
key factors that are leading to successful tree regeneration is
challenging. Currently, tree regeneration processes in dynamic forest
models are handled in a multitude of ways [@konig_tree_2022;
@bugmann2022]: from 1) entirely ignoring it [as done in classical forest
growth models, e.g., Pretzsch et al. -@pretzsch2002], across 2) the use
of a few simple environmental filters, as done in most forest "gap"
models [@shugart1984] and Dynamic Global Vegetation Models [e.g.,
@hickler2012; @smith2001], to 3) complex approaches that incorporate
local feedback from the canopy, multiple ecological processes and often
also short time steps [e.g., @seidl2012; @wehrli2006], or 4) field-based
statistical parameterizations, which however are not easy to extrapolate
in space and time [e.g., @ribbens1994].

Overall, models are needed to (1) synthesize existing empirical data and
explore their relationships, (2) assess future tree regeneration e.g. in
the context of global change scenarios, and (3) identify the most
important processes that are shaping ecological patterns. Given the
current strategies that are used in models of forest dynamics to
represent tree regeneration, model behavior often is prone to problems,
such as very high levels of tree regeneration that necessitate excess
mortality at early stages of tree life to simulate correct stand
structure and composition. Also, inadequately high species diversity in
tree regeneration may be simulated, which is characteristic of
"classical" forest gap models [@gutiérrez2016], at least as long as the
simulation set-up comprises a multitude of species. Some models use
calibration against local canopy-level data to constrain simulated
regeneration levels, which is likely to hamper the general applicability
of these models e.g. under scenarios of climate change. Furthermore,
correctly capturing the species composition in tree regeneration as a
function of the presence of seed trees in the canopy is often a
particular challenge, potentially leading to unrealistic successional
drift in the model, which must be corrected by factors that are hard to
parameterize [e.g., @lischke2006]. A related issue is the excessive
reduction of species diversity due to positive feedback effects, such
that eventually just single-species stands remain. This is sometimes
corrected by the incorporation of a low level of seed influx of all
species at all times [@schumacher2006] or by restricting the number of
seeds per species in the seedbank [@lischke2006]. However, simulated
species composition is usually exceedingly sensitive to assumptions
about seed availability, whereas the parameters of such functions are
poorly constrained by field data. Lastly, there is often a problem with
insufficient observational constraints on parameter values for models
that start from very small tree sizes (e.g., 10 cm of height or even
seeds) and track tree development in a process-oriented manner by
considering a multitude of ecological influences, rather than
emphasizing tree regeneration into a larger size class [e.g.,
@wehrli2006].

@@

```{r mortality13, echo=FALSE, fig.cap="Ratio of tree regeneration between the 7 and 10 cm thresholds (regeneration 7 cm / regeneration 10 cm) and the overestimation proportion at 7 cm ([simulated - observed] / observed) for the mean regeneration per model across sites and samples. The horizontal dashed lines show a ratio equal to 1, indicating no decrease of regeneration between 7 and 10 cm, and a ratio equal to 1.77 corresponding to the Reineke self-thinning line under even-aged conditions. The vertical line indicates zero overestimation.", out.width='80%'}
knitr::include_graphics(here::here("figures", "mort7_10_medianOver.png"))
```
